---
title: "For_Benny"
author: "Ruijuan Li"
date: "11/28/2017"
output: html_document
---

### import lib
```{r}
library(tidyverse)
library(qtl)
```

### load geno data 
```{r}
## Maternal 
load("~/Documents/backupCIP/QTLs/Potato_QTLs/BennyOnlyMatchM.Rdata") 

BennyOnlyMatchM %>% dim()  # 348 196
class(BennyOnlyMatchM)
<<<<<<< HEAD
# View(BennyOnlyMatchM)
=======
View(BennyOnlyMatchM)
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

# Format Maternal genotypic data 
colnames(BennyOnlyMatchM)
BennyOnlyMatchM.1 <- 
BennyOnlyMatchM %>% 
  mutate(id = Locus_ID) %>% 
  dplyr::select(id, LG, GM_POS, G1:G180) 

<<<<<<< HEAD
colnames(BennyOnlyMatchM.1) 

# keep LG 1-12
BennyOnlyMatchM.2 <- BennyOnlyMatchM.1[BennyOnlyMatchM.1$LG != "13",]
sum(BennyOnlyMatchM.1$LG == 13)
dim(BennyOnlyMatchM.2) # 346 183 
BennyOnlyMatchM.2[1:10, 1:10]

# modify geno file again to make it same have the same format as the sample data from r/qtl 
BennyOnlyMatchM.2 <- as.data.frame(t(BennyOnlyMatchM.2)) 
# http://www.rqtl.org/sampledata/listeria_gen.csv make sure your file looks the same as the file shows here 
write.csv(BennyOnlyMatchM.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchM.2.csv")

# paternal 
=======
# keep LG 1-12
BennyOnlyMatchM.2 <- BennyOnlyMatchM.1[BennyOnlyMatchM.1$LG != "13",]

write.csv(BennyOnlyMatchM.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchM.2.csv", row.names = FALSE)
# modify the colname manually 

# paternal
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
load("~/Documents/backupCIP/QTLs/Potato_QTLs/BennyOnlyMatchP.Rdata")

BennyOnlyMatchP %>% dim()  # 317 196
class(BennyOnlyMatchP)

# Format Paternal genotypic data 
colnames(BennyOnlyMatchP)
BennyOnlyMatchP.1 <- 
BennyOnlyMatchP %>% 
  mutate(id = Locus_ID) %>% 
  dplyr::select(id, LG, GM_POS, G1:G180) 

# keep only LG 1-12
BennyOnlyMatchP.2 <- BennyOnlyMatchP.1[BennyOnlyMatchP.1$LG != "13",]

<<<<<<< HEAD
# modify geno file again to make it same have the same format as the sample data from r/qtl 
BennyOnlyMatchP.2 <- as.data.frame(t(BennyOnlyMatchP.2)) 
# http://www.rqtl.org/sampledata/listeria_gen.csv make sure your file looks the same as the file shows here 

write.csv(BennyOnlyMatchP.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchP.2.csv") 
# modify the colname manually remove LG and GM_POS from the file 
# Do not re-run the above code, just use the save object !!! 
=======

write.csv(BennyOnlyMatchP.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchP.2.csv", row.names = FALSE) 
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
```

### Load pheno data and reformat 
```{r}
pheno.Benny <- read.csv("~/Documents/backupCIP/QTLs/Potato_QTLs/data/Total_phenotypicData-RBs.csv")
pheno.Benny %>% head()

pheno.Benny$id <- paste("G", pheno.Benny$Individual, sep = "")

pheno.Benny.2 <- 
pheno.Benny %>% 
  dplyr::select(-(CIP.NUMBER:Individual)) %>% 
  t() %>% 
  as.data.frame()

<<<<<<< HEAD
# modify geno file again to make it same have the same format as the sample data from r/qtl 
pheno.Benny.2 <- as.data.frame(t(pheno.Benny.2)) 
# http://www.rqtl.org/sampledata/listeria_phe.csv make sure your file looks the same as the file shows here 

write.csv(pheno.Benny.2, "~/Documents/backupCIP/QTLs/Potato_QTLs/data/pheno.Benny.2.csv", row.names = FALSE) 
```

# Start mapping 
```{r}

# Maternal Version
LG.Benny.M <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchM.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("ll", "lm"), na.strings = c("--"), BC.gen = 1) 
=======
write.csv(pheno.Benny.2, "~/Documents/backupCIP/QTLs/Potato_QTLs/data/pheno.Benny.2.csv", row.names = TRUE) 
```

### combine geno and pheno to one file (maybe for later...)
```{r}
test3 <- read.csv("~/Documents/backupCIP/QTLs/Potato_QTLs/data/pheno.Benny.2.csv")
dim(test3) #13 181
```

# start mapping 
```{r}
# Maternal Version
LG.Benny.M <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchM.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("ll", "lm"), na.strings = c("--"), BC.gen = 1) # first try to use just one map, for test purpose  

LG.Benny.M <- jittermap(LG.Benny.M) 
LG.Benny.M$pheno %>% dim() # 184 13 

# takes about a minute to estimate the map
summary(LG.Benny.M) 
summaryMap(LG.Benny.M)
plotMap(LG.Benny.M) 
plot.rf(LG.Benny.M) 

# Paternal Version
LG.Benny.P <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchP.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("nn", "np"), na.strings = c("--"), BC.gen = 1) # first try to use just one map, for test purpose  

LG.Benny.P <- jittermap(LG.Benny.P) 
LG.Benny.P$pheno %>% dim() # 184 13 
LG.Benny.P$geno$`13`$data %>% dim() # 50 markers 

# takes about a minute to estimate the map
summary(LG.Benny.P) 
summaryMap(LG.Benny.P) 
plotMap(LG.Benny.P) 
plot.rf(LG.Benny.P)  
save(LG.Benny.P, file = "~/Desktop/LG.Benny.P.Rdata")
```

### Just get the markers from 12 LGs (1 -12)
```{r}

####(!!)#####
### load geno data 

## Maternal 
load("~/Documents/backupCIP/QTLs/Potato_QTLs/BennyOnlyMatchM.Rdata") 

BennyOnlyMatchM %>% dim()  # 348 196
class(BennyOnlyMatchM)
View(BennyOnlyMatchM)

# Format Maternal genotypic data 
colnames(BennyOnlyMatchM)
BennyOnlyMatchM.1 <- 
BennyOnlyMatchM %>% 
  mutate(id = Locus_ID) %>% 
  dplyr::select(id, LG, GM_POS, G1:G180) 

# keep LG 1-12
BennyOnlyMatchM.2 <- BennyOnlyMatchM.1[BennyOnlyMatchM.1$LG != "13",]

write.csv(BennyOnlyMatchM.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchM.2.csv", row.names = FALSE)
# modify the colname manually 

# paternal
load("~/Documents/backupCIP/QTLs/Potato_QTLs/BennyOnlyMatchP.Rdata")

BennyOnlyMatchP %>% dim()  # 317 196
class(BennyOnlyMatchP)

# Format Paternal genotypic data 
colnames(BennyOnlyMatchP)
BennyOnlyMatchP.1 <- 
BennyOnlyMatchP %>% 
  mutate(id = Locus_ID) %>% 
  dplyr::select(id, LG, GM_POS, G1:G180) 

# keep only LG 1-12
BennyOnlyMatchP.2 <- BennyOnlyMatchP.1[BennyOnlyMatchP.1$LG != "13",]


write.csv(BennyOnlyMatchP.2, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/data/BennyOnlyMatchP.2.csv", row.names = FALSE) 
```

### Load pheno data and reformat 
```{r}
pheno.Benny <- read.csv("~/Documents/backupCIP/QTLs/Potato_QTLs/data/Total_phenotypicData-RBs.csv")
pheno.Benny %>% head()

pheno.Benny$id <- paste("G", pheno.Benny$Individual, sep = "")

pheno.Benny.2 <- 
pheno.Benny %>% 
  dplyr::select(-(CIP.NUMBER:Individual)) %>% 
  t() %>% 
  as.data.frame()

write.csv(pheno.Benny.2, "~/Documents/backupCIP/QTLs/Potato_QTLs/data/pheno.Benny.2.csv", row.names = TRUE) 
```

### combine geno and pheno to one file (maybe for later...)
```{r}
test3 <- read.csv("~/Documents/backupCIP/QTLs/Potato_QTLs/data/pheno.Benny.2.csv")
dim(test3) 
```

# start mapping 
```{r}
# Maternal Version
LG.Benny.M <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchM.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("ll", "lm"), na.strings = c("--"), BC.gen = 1) # first try to use just one map, for test purpose  
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

LG.Benny.M <- jittermap(LG.Benny.M) 
LG.Benny.M$pheno %>% dim() # 184 13 

# takes about a minute to estimate the map
summary(LG.Benny.M) 
summaryMap(LG.Benny.M)
plotMap(LG.Benny.M) 
plot.rf(LG.Benny.M) 

# Paternal Version
<<<<<<< HEAD
LG.Benny.P <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchP.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("nn", "np"), na.strings = c("--"), BC.gen = 1) 
=======
LG.Benny.P <- read.cross(format = "csvsr", dir = "~/Documents/backupCIP/QTLs/Potato_QTLs/data", genfile = "BennyOnlyMatchP.2.csv", phefile = "pheno.Benny.2.csv", genotypes = c("nn", "np"), na.strings = c("--"), BC.gen = 1) # first try to use just one map, for test purpose  
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

LG.Benny.P <- jittermap(LG.Benny.P) 
LG.Benny.P$pheno %>% dim() # 184 13 
LG.Benny.P$geno$`13`$data %>% dim() # 50 markers 

<<<<<<< HEAD
# takes ~1 min to estimate the Map
=======
# takes about a minute to estimate the map
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
summary(LG.Benny.P) 
summaryMap(LG.Benny.P) 
plotMap(LG.Benny.P) 
plot.rf(LG.Benny.P)     
save(LG.Benny.P, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.P.Rdata")
save(LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.M.Rdata")
```

<<<<<<< HEAD
### Scanone on all traits 
```{r}
# To see where are you

getwd()

#Load libraries
=======
### scanone on all traits 
```{r}
## To see where are you

getwd()

>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
library(qtl)
library(tidyverse)

#load my files
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.P.Rdata")
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.M.Rdata")

<<<<<<< HEAD
#I am following 'CSHL_QTL.R'file
#let's try making a new map 
=======
##following 'CSHL_QTL.R'file
#let's create a new map  
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
newmapLG.Benny.P <- est.map(LG.Benny.P,verbose=T,error.prob=.01)
newmapLG.Benny.M <- est.map(LG.Benny.M,verbose=T,error.prob=.01)

#compare the old and new maps
plot.map(newmapLG.Benny.P,LG.Benny.P)
plot.map(newmapLG.Benny.M,LG.Benny.M)

###Here we can see a comparison of both 

plot(newmapLG.Benny.M, LG.Benny.M, col= c("red", "purple"))
plot(newmapLG.Benny.P, LG.Benny.P, col= c("red", "purple"))

<<<<<<< HEAD
#because we know the general linkage between markers we can look for possible genotyping errors.
=======
#because we know the general linkage between markers we can 
#look for possible genotyping errors.
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
#calculate the probability of genotyping errors

LG.Benny.P <- calc.errorlod(LG.Benny.P, error.prob=0.01)
LG.Benny.M <- calc.errorlod(LG.Benny.M, error.prob=0.01)

#look at a table of results
top.errorlod(LG.Benny.P)
top.errorlod(LG.Benny.M)

#plot results
plot.errorlod(LG.Benny.P) 
plot.errorlod(LG.Benny.M)

#this reveals two possible errors in individuals.
#Read more about this!. Hoping that there isnt enough to worry about.
<<<<<<< HEAD
#Do not need use a new map, just work with the first one
=======

>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

#If a lot of errors were revealed then it would be worth rechecking
  #the data

#Check that I have my columns named correctly
colnames(LG.Benny.M$pheno)
colnames(LG.Benny.P$pheno)

#Eliminate "v1"and "id" in both
LG.Benny.M$pheno <- 
LG.Benny.M$pheno %>% 
  dplyr::select(-V1, -id) 

LG.Benny.P$pheno <- 
LG.Benny.P$pheno %>% 
  dplyr::select(-V1, -id) 

sapply(colnames(LG.Benny.M$pheno), function(x) class(LG.Benny.M$pheno[,x]))
sapply(colnames(LG.Benny.P$pheno), function(x) class(LG.Benny.P$pheno[,x]))

LG.Benny.M$pheno <- 
as.data.frame(sapply(colnames(LG.Benny.M$pheno), function(x) as.numeric(as.character(LG.Benny.M$pheno[,x])))) 

LG.Benny.P$pheno <- 
as.data.frame(sapply(colnames(LG.Benny.P$pheno), function(x) as.numeric(as.character(LG.Benny.P$pheno[,x])))) 

<<<<<<< HEAD
#Then, we calculate genotype probabilities at "virtual" loci between our real markers two different methods are used because the downstream mapping methods require different estimates here 

LG.Benny.P <- sim.geno(LG.Benny.P,step=1,n.draws=32)
LG.Benny.M <- sim.geno(LG.Benny.M,step=1,n.draws=32)
#Uses imputation

  #Creates n.draw number of populations where the missing genotypes are filled in based on recombination frequencies

=======
#next we calculate genotype probabilities at "virtual" loci between our real markers
#two different methods are used because the downstream mapping methods require different
#estimates here 

LG.Benny.P <- sim.geno(LG.Benny.P,step=1,n.draws=32)
LG.Benny.M <- sim.geno(LG.Benny.M,step=1,n.draws=32)
#uses imputation
  #creates n.draw number of populations where the missing genotypes are filled in based on 
  #recombination frequencies
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
LG.Benny.P <- calc.genoprob(LG.Benny.P,step=1)
LG.Benny.M <- calc.genoprob(LG.Benny.M,step=1)
#just calculates the probabilities at different locations

<<<<<<< HEAD
###Let's Map 

#Start by doing a one dimensional scan on imputed genotypes
=======
###Let's map 
#start by doing a one dimensional scan on imputed genotypes
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

#Run scanone with method ="em", "em" stands for interval mapping
out.em.LG.Benny.M <- scanone(LG.Benny.M, pheno.col = 1:12, method = "em")
out.em.LG.Benny.P <- scanone(LG.Benny.P, pheno.col = 1:12, method = "em")

#Run scanone with method ="mr", "mr" stands for marker regresion
out.mr.LG.Benny.M <- scanone(LG.Benny.M, pheno.col = 1:12, method = "mr")
out.mr.LG.Benny.P <- scanone(LG.Benny.P, pheno.col = 1:12, method = "mr")

# Let's pull out the single largest LOD score from each chromosome
# Check for those having LOD > 3
summary(out.mr.LG.Benny.M, threshold=3)
summary(out.mr.LG.Benny.P, threshold=3)
#seems that any of them have it. 
<<<<<<< HEAD
=======
#maybe later
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

#Function max.scanone may be used to pick out the single biggest LOD score, as follows. 
max(out.mr.LG.Benny.M)
max(out.mr.LG.Benny.P)
max(out.em.LG.Benny.M)
max(out.mr.LG.Benny.P)
#maybe later

#Permute the data to set a signficance threshold 
#use method="imp" because "imp" is better for missing genotype data

scanone.perm.LG.Benny.P <- scanone(LG.Benny.P, pheno.col = 1:12, method="imp",n.perm=1000) 
scanone.perm.LG.Benny.M <- scanone(LG.Benny.M, pheno.col = 1:12, method="imp",n.perm=1000) 
<<<<<<< HEAD

#Save file to be able to load them later
save(scanone.perm.LG.Benny.P, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scanone.perm.LG.Benny.P.Rdata")

save(scanone.perm.LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scanone.perm.LG.Benny.M.Rdata")
 #takes about 2 hours each

load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scanone.perm.LG.Benny.P.Rdata")
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scanone.perm.LG.Benny.M.Rdata")
=======
 #takes about 10 minutes each
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

# Summary of our permutations
summary(scanone.perm.LG.Benny.P)
summary(scanone.perm.LG.Benny.M)

<<<<<<< HEAD
perm95.LG.Benny.P <- summary(scanone.perm.LG.Benny.P)
perm95.LG.Benny.M <- summary(scanone.perm.LG.Benny.M)
=======
perm95.LG.Benny.M <- summary(scanone.perm.LG.Benny.M)
perm95.LG.Benny.P <- summary(scanone.perm.LG.Benny.P)
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
#keep the 95th percentile for future use.
#This corresponds to p <0.05

#note method "em" = interval mapping; "mr" = marker regression
#here we use method "imp" for multiple imputation.
  #advantage of "imp" is better for missing genotype data
<<<<<<< HEAD
  #disadvantage of "imp" is that it is slower.
scanone.imp.LG.Benny.M <- scanone(LG.Benny.M, pheno.col=1:12, method="imp")
plot(scanone.imp.LG.Benny.M[,c(1,2,14)], col = "purple",main="Scanone.imp.LG.Benny Maternal")
abline(h=perm95.LG.Benny.M[1,1],lty=2:6) #add permutation threshold

scanone.imp.LG.Benny.P <- scanone(LG.Benny.P, pheno.col=1:12, method="imp")
plot(scanone.imp.LG.Benny.P[,c(1,2,14)], col="purple", main="Scanone.imp.LG.Benny Paternal")
abline(h=perm95.LG.Benny.P[1,1],lty=2:6) #add permutation threshold

```

```{r}

```

### CIM on all traits 
```{r}

#Check where are you
getwd()
setwd("/Users/bordonez/Documents/BackupCIP/QTLs/Potato_QTLs/analysis")

# load your libraries
library(qtl)
library(tidyverse)

#Load your previous files
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.P.Rdata")
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.M.Rdata")

=======
  #disadvantage is that it is slower.
scanone.imp.LG.Benny.M <- scanone(LG.Benny.M, pheno.col=1:12, method="imp")
plot(scanone.imp.LG.Benny.M[,c(1,2,14)], bandcol="gray90", main="Scanone.imp.LG.Benny Maternal")
abline(h=perm95.LG.Benny.M[1,1],lty=2:6) #add permutation threshold

scanone.imp.LG.Benny.P <- scanone(LG.Benny.P, pheno.col=1:12, method="imp")
plot(scanone.imp.LG.Benny.P[,c(1,2,14)], bandcol="gray90", main="Scanone.imp.LG.Benny Paternal")
abline(h=perm95.LG.Benny.P[1,1],lty=2:6) #add permutation threshold

```
### CIM on all traits 
```{r}
#

library(qtl)
library(tidyverse)

>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
#cim
#First assign according the data 
colnames(LG.Benny.M$pheno)

cim.LG.Benny.M <- 
lapply(seq_along(1: ncol(LG.Benny.M$pheno)), function(trait) {
  print(trait)
  LG.Benny.M$pheno <- as.data.frame(LG.Benny.M$pheno[,trait])
  cim(LG.Benny.M, n.marcovar=5,method="imp")
}) 

<<<<<<< HEAD

=======
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
colnames(LG.Benny.P$pheno)
cim.LG.Benny.P <- 
lapply(seq_along(1: ncol(LG.Benny.P$pheno)), function(trait) {
  print(trait)
  LG.Benny.P$pheno <- as.data.frame(LG.Benny.P$pheno[,trait])
  cim(LG.Benny.P, n.marcovar=5,method="imp")
}) 


#the n.marcovar= argument defines the maximum number of marker covariates to use.

cim.LG.Benny.M.20 <- lapply(seq_along(1: ncol(LG.Benny.M$pheno)), function(trait) {
  print(trait)
  LG.Benny.M$pheno <- as.data.frame(LG.Benny.M$pheno[,trait])
  cim(LG.Benny.M,n.marcovar=5,window=20,method="imp", error.prob = 0.001)
}) 

cim.LG.Benny.M.40 <- lapply(seq_along(1: ncol(LG.Benny.M$pheno)), function(trait) {
  print(trait)
  LG.Benny.M$pheno <- as.data.frame(LG.Benny.M$pheno[,trait])
  cim(LG.Benny.M,n.marcovar=5,window=40,method="imp", error.prob = 0.001)
}) 

cim.LG.Benny.M.Inf <- lapply(seq_along(1: ncol(LG.Benny.M$pheno)), function(trait) {
  print(trait)
  LG.Benny.M$pheno <- as.data.frame(LG.Benny.M$pheno[,trait])
  cim(LG.Benny.M,n.marcovar=5,window=Inf,method="imp", error.prob = 0.001)
}) 

<<<<<<< HEAD

=======
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
cim.LG.Benny.P.20 <- 
lapply(seq_along(1: ncol(LG.Benny.P$pheno)), function(trait) {
  print(trait)
  LG.Benny.P$pheno <- as.data.frame(LG.Benny.P$pheno[,trait])
  cim(LG.Benny.P,n.marcovar=5,window=20,method="imp", error.prob = 0.001)
}) 

<<<<<<< HEAD

=======
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
cim.LG.Benny.P.40 <- 
lapply(seq_along(1: ncol(LG.Benny.P$pheno)), function(trait) {
  print(trait)
  LG.Benny.P$pheno <- as.data.frame(LG.Benny.P$pheno[,trait])
  cim(LG.Benny.P,n.marcovar=5,window=40,method="imp", error.prob = 0.001)
}) 

cim.LG.Benny.P.Inf <- 
lapply(seq_along(1: ncol(LG.Benny.P$pheno)), function(trait) {
  print(trait)
  LG.Benny.P$pheno <- as.data.frame(LG.Benny.P$pheno[,trait])
  cim(LG.Benny.P,n.marcovar=5,window=Inf,method="imp", error.prob = 0.001)
}) 


#Summary of cim
summary(cim.LG.Benny.M[[1]])
summary(cim.LG.Benny.P[[1]])

#Check the maximun LOD score
<<<<<<< HEAD
max(cim.LG.Benny.M[[1]][,3]) #2.69
max(cim.LG.Benny.P[[1]][,3]) #2.82

max(cim.LG.Benny.M.20[[1]][,3]) #1.66
max(cim.LG.Benny.P.20[[1]][,3]) #2.65
max(cim.LG.Benny.M.40[[1]][,3]) #1.76
max(cim.LG.Benny.P.40[[1]][,3]) #3.29
max(cim.LG.Benny.M.Inf[[1]][,3]) #1.69
max(cim.LG.Benny.P.Inf[[1]][,3]) #2.08
=======
max(cim.LG.Benny.M[[1]][,3]) #2.30
max(cim.LG.Benny.P[[1]][,3]) #2.66

max(cim.LG.Benny.M.20[[1]][,3]) #1.86
max(cim.LG.Benny.P.20[[1]][,3]) #2.25
max(cim.LG.Benny.M.40[[1]][,3]) #1.94
max(cim.LG.Benny.P.40[[1]][,3]) #3.14
max(cim.LG.Benny.M.Inf[[1]][,3]) #1.79
max(cim.LG.Benny.P.Inf[[1]][,3]) #1.86
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651


##Plot out cim results
plot(cim.LG.Benny.P[[1]], ylab="LOD score", col = "blue", main="cim LG. Paternal Map")
<<<<<<< HEAD
add.cim.covar(cim.LG.Benny.P[[1]], col="red") # add dots indicating the locations of the selected marker covariates.
abline(h=max(cim.LG.Benny.P[[1]][,3]),lty=2:6) #add permutation threshold

plot(cim.LG.Benny.M[[1]], ylab="LOD score", col = "blue", main="cim LG. Maternal Map") 
add.cim.covar(cim.LG.Benny.M[[1]], col="red") #add dots indicating the locations of the selected marker covariates.
abline(h=max(cim.LG.Benny.M[[1]][,3]),lty=2:6) #add permutation threshold
=======
abline(h=max(cim.LG.Benny.P[[1]][,3]),lty=2:6) #add permutation threshold

plot(cim.LG.Benny.M[[1]], ylab="LOD score", col = "blue", main="cim LG. Maternal Map") 
abline(h=max(cim.LG.Benny.M[[1]][,3]),lty=2) #add permutation threshold
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651


##Plot out Paternal Map results with every window, along with the LOD scores obtained by cim
par(mfrow=c(3,1))
plot(cim.LG.Benny.P[[1]],cim.LG.Benny.P.20[[1]], ylab="LOD score", col= c("green","blue"), main="Paternal Map, window = 20 cM")
add.cim.covar(cim.LG.Benny.P.20[[1]], chr =chr, col="red")
abline(h=max(cim.LG.Benny.P[[1]][,3]),lty=2:6)
plot(cim.LG.Benny.P[[1]],cim.LG.Benny.P.40[[1]], ylab="LOD score", col= c("green","blue"), main="Paternal Map, window = 40 cM")
add.cim.covar(cim.LG.Benny.P.40[[1]], chr =chr, col="red")
abline(h=max(cim.LG.Benny.P[[1]][,3]),lty=2:6)
plot(cim.LG.Benny.P[[1]],cim.LG.Benny.P.Inf[[1]], ylab="LOD score", col= c("green","blue"), main="Paternal Map, window = Inf cM")
add.cim.covar(cim.LG.Benny.P.Inf[[1]], col="red")
abline(h=max(cim.LG.Benny.P[[1]][,3]),lty=2:6)
dev.off()

##Plot out Maternal Map results with every window, along with the LOD scores obtained by cim
par(mfrow=c(3,1))
plot(cim.LG.Benny.M[[1]],cim.LG.Benny.M.20[[1]], ylab="LOD score", col= c("green","blue"), main="Maternal Map, window = 20 cM")
add.cim.covar(cim.LG.Benny.M.20[[1]], col="red")
abline(h=max(cim.LG.Benny.M[[1]][,3]),lty=2:6)
plot(cim.LG.Benny.M[[1]],cim.LG.Benny.M.40[[1]], ylab="LOD score", col= c("green","blue"), main="Maternal Map, window = 40 cM")
add.cim.covar(cim.LG.Benny.M.40[[1]], col="red")
abline(h=max(cim.LG.Benny.M[[1]][,3]),lty=2:6)
plot(cim.LG.Benny.M[[1]],cim.LG.Benny.M.Inf[[1]], ylab="LOD score", col= c("green","blue"), main="Maternal Map, window = Inf cM")
add.cim.covar(cim.LG.Benny.M.Inf[[1]], col="red")
abline(h=max(cim.LG.Benny.M[[1]][,3]),lty=2:6)
dev.off()

#Run cim n.permutations = 1000. Run for each trait
<<<<<<< HEAD
cim.perm.LG.Benny.P <- cim(LG.Benny.P,n.marcovar=5,method="imp",n.perm=1000)

save(cim.perm.LG.Benny.P, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/cim.perm.LG.Benny.P")

cim.perm.LG.Benny.M <- cim(LG.Benny.M,n.marcovar=5,method="imp",n.perm=1000)
#will take time ~10 min each. 

save(cim.perm.LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/cim.perm.LG.Benny.M")

#Summary, shows the 90th and 95th percentile of LOD scores in randomized data
summary(cim.perm.LG.Benny.P) #5%: 3.85; 10% 3.33
summary(cim.perm.LG.Benny.M) #5%: 4.32; 10% 3.71

#Keep the 95th percentile for future use. This corresponds to p <0.05
cim.perm95.LG.Benny.P <- summary(cim.perm.LG.Benny.P)[1] #3.90
cim.perm95.LG.Benny.M <- summary(cim.perm.LG.Benny.M)[1] #4.10
=======

cim.perm.LG.Benny.P <- cim(LG.Benny.P,n.marcovar=5,method="imp",n.perm=1000)
cim.perm.LG.Benny.M <- cim(LG.Benny.M,n.marcovar=5,method="imp",n.perm=1000)
#will take time ~10 min each. 

#Summary, shows the 90th and 95th percentile of LOD scores in randomized data
summary(cim.perm.LG.Benny.P) #5%: 3.96; 10% 3.47
summary(cim.perm.LG.Benny.M) #5%: 3.85; 10% 3.50

#Keep the 95th percentile for future use. This corresponds to p <0.05
cim.perm95.LG.Benny.P <- summary(cim.perm.LG.Benny.P)[1] #3.95
cim.perm95.LG.Benny.M <- summary(cim.perm.LG.Benny.M)[1] #3.85
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

#Plot out results
plot(cim.LG.Benny.P[[1]],ylab="LOD score", main="cim.perm.LG.Paternal Map")
abline(h=cim.perm95.LG.Benny.P,lty=2:6) #add permutation threshold 

plot(cim.LG.Benny.M[[1]],ylab="LOD score", main="cim.perm. LG.Maternal Map")
abline(h=cim.perm95.LG.Benny.M,lty=2:6) #add permutation threshold 


<<<<<<< HEAD
#Save correctly
save(LG.Benny.P, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.P.Rdata")
save(LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.M.Rdata")
```
=======
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651
##A 2D scan
#The above methods only evaluate the evidence for a QTL one location a time. 
#It is possible to instead scan two locations at once. 
#This can be particularly advantageous in identifying QTL if there is epistasis.
<<<<<<< HEAD
```{r}
#Load my files

load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.P.Rdata")
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/LG.Benny.M.Rdata")

scantwo.imp.LG.Benny.P <- scantwo(LG.Benny.P,method="imp",verbose=T) 
scantwo.imp.LG.Benny.M <- scantwo(LG.Benny.M,method="imp",verbose=T) 
#takes 30 minutes each

save(scantwo.imp.LG.Benny.P, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.LG.Benny.P.Rdata")
save(scantwo.imp.LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.LG.Benny.M.Rdata")

#Load data
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.LG.Benny.P.Rdata")
load("~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.LG.Benny.M.Rdata")


#Let's see the graphic to have an idea 
plot(scantwo.imp.LG.Benny.M, chr = 1:12, main = "LG.Maternal Map")
plot(scantwo.imp.LG.Benny.P, chr = 1:12, main = "LG.Paternal Map")
=======

#scantwo.imp.LG.Benny.P <- scantwo(LG.Benny.P,method="imp",verbose=T) 
#scantwo.imp.LG.Benny.M <- scantwo(LG.Benny.M,method="imp",verbose=T) 
#takes 4 minutes each

#Let's see the graphic to have an idea 
#plot(scantwo.imp.LG.Benny.M, chr = 1:12, main = "LG.Maternal Map")
#plot(scantwo.imp.LG.Benny.P, chr = 1:12, main = "LG.Paternal Map")
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

#permutations take a long time, about 2 hours for 1000? 
#scantwo.imp.perm.LG.Benny.P <- scantwo(LG.Benny.P,method="imp",verbose=T,n.perm=1000) 
#save(scantwo.imp.perm.LG.Benny.P,file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.perm.LG.Benny.P.Rdata")

#scantwo.imp.perm.LG.Benny.M <- scantwo(LG.Benny.M,method="imp",verbose=T,n.perm=1000) 
#save(scantwo.imp.perm.LG.Benny.M, file = "~/Documents/backupCIP/QTLs/Potato_QTLs/analysis/scantwo.imp.perm.LG.Benny.M.Rdata")

#load the pre-run permutations
#load("scantwo.imp.perm.LG.Benny.P.Rdata")
#load("scantwo.imp.perm.LG.Benny.M.Rdata")

#summary(scantwo.imp.perm.LG.Benny.P)
#summary(scantwo.imp.perm.LG.Benny.M)

#plot(scantwo.imp.perm.LG.Benny.M)
#plot(scantwo.imp.perm.LG.Benny.P)

#There are many different models being considered in the 2D models.  
#The LOD scores reflect the following comparisons
#columns:
  #full 2 QTL w/ interaction vs. null model
  #fv1 2 QTL w/ interaction vs 1 QTL
  #int 2 QTL w/interaction vs 2 QTL additive. (test for interaction)
  #add 2 QTL additive vs null model
  #av1 2 QTL additive vs 1 QTL (test for 2nd QTL if additive)
  #one 1 QTL model vs null

#summary(scantwo.imp.LG.Benny.M,perm.M=scantwo.imp.perm.LG.Benny.M,pvalues=T)

#plot(scantwo.imp.LG.Benny.M,zscale=T) 
      #upper compares model for 2 QTL with interaction to 2 QTL additive
          #(evidence for interaction); corresponds to "int" above
      #lower compares 2 QTL interaction with no QTL 
          #(evidence for QTL); corresponds to "full" above

```

<<<<<<< HEAD
```{r}

```

=======
>>>>>>> 0beaa2b6f662aa0b69c4217a1b0ed9eabd3c9651

